A large-scale study of polymorphism in R

### 2019-03-15 paper/main.tex
intro wip

>>>>

A number of programming languages have gained popularity for data science
tasks, they include MATLAB, Python, Julia and R.

These languages are all dynamically typed.

This is because they emphasize ease of programming, interactive data
exploration, and light-weight syntax.

To faciliate programming these language offer all kinds of short cuts and
facilities that increase the likelyhood that code will ``just work''.

For example abbreviation of name arguments and automatic conversions.

But invariably some applications written in those languages survive past the prototype stage.

The results obtained are published and even sometimes drive policy decisions.

Given that code almost never stops, and that any computation is likely to deliver a bunch of numbers, how can we trust those numbers?

Years of work in programming languages suggest that one cost efficient way to catch some errors is to add types to a language.

In the last decade much attention has been given to the incremental addition of types. Successes like Hack, TypeScript and Racket suggest that this may be feasible for wide spectrum languages.
